\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Sparse Communication for Deep Learning}
\author{Kelly (Thesis)}
\date{May 2020}

\begin{document}

\maketitle




\section{Chapter 1 - Introduction}

\subsection{Which problem are you solving in this thesis?}
Explain

\subsection{Why is it an important problem?}
 Explain
 
\subsection{What has been done in the past for that particular problem?}
Explain

\subsection{What are YOU proposing?}
Explain

\subsection{Why is your solution better than existing ones?}
Explain


\section{Chapter 2 - Background}

\subsection{Distributed machine learning and SGD}
Similar to Section II from GRACE. You can add more details. Aritra has a more detailed (older) version. Ask him.  

\subsection{Compressed communication}
Similar to first paragraph of GRACE-Section III. Add a lot of details for Sparcification ONLY.

\subsection{Bit compression}

\subsubsection{Run length encoding}
Here you may add a few sentences about other compression schemes similar to RLE.

\subsubsection{Bloom filters}

\subsection{Curve fitting}




\section{Chapter 3 - Related work}

\subsection{Other compression methods}
Quantization, Hybrid and Low-rank. Use the material from GRACE-Section III, but LESS details.

\subsection{Related topics}
Use the material from GRACE-Section VI. Add MORE details. Aritra has a more detailed (older) version. Ask him.



\section{Chapter 4 - Compressing the tensor indices}
COPY-PASTE from Kelly-paper 2


\section{Chapter 5 - Fitting the tensor values}
COPY-PASTE from Kelly-paper 1

\section{Conclusions and Future Work}

\end{document}
